Cosmological Evidences of Dark Matter through the CMB

### 2018-12-23 paper/main.tex
baryonic effect

\section{Introduction}
-brief thermal history of the universe and how to get to the cmb and what is it?\\
-practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
which info can we get from the cmb: Big bang, maater and energy content of the universe---dark matter is a big part of the matter content it influenced the spectrum  of the CMB ---- so it played a role.\\
-structure of the paper \\

@@

\section{From the Discovery of the CMB to the Planck mission}
\citep{bucherPhysicsCosmicMicrowave2015}
-discovery of the cmb
-filterng of the images
-different missions

>>>>

\section{Introduction}
-\citep{WayneHu} brief thermal history of the universe and how to get to the cmb and what is it?\\
-practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
which info can we get from the cmb: Big bang, maater and energy content of the universe---dark matter is a big part of the matter content it influenced the spectrum  of the CMB ---- so it played a role.\\
-structure of the paper \\

@@

\section{From the Discovery of the CMB to the Planck mission}
\citep{bucherPhysicsCosmicMicrowave2015}
-discovery of the cmb\\
-filterng of the images\\
-different missions\\

\section{Content of the Universe}
\begin{itemize}
\item Assumptions: working with the $\Lambda$CDM model
\item General relativty
\item Friedmann equations
\end{itemize}

\section{CMB theo analysis}
\begin{itemize}
\item hydrodynamics \citep{huLectureNotesCMB2008}
page 14 eq 49 to page 17 eq 71\\
skip doppler effect
\item gravito acoustic oscillations page 19 up to eq 82 , justify briefly constant potential in page 20
% if stress perturbations are negligible compared with density perturbations ( δp ≪ δρ ) then the potential will remain constant in periods where the background equation of state p/ρ is constant
\item page 20 and 21 up to eq92 important comment 
%The consequence is that overdense regions where Ψ is negative (potential wells) are cold spots in the effective temperature.
\item baryonic effect
\end{itemize}
hydrodinamics
